A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-08 main.tex
Updates from Overleaf

%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of fear, depression, stress, anxiety, fatigue, sadness, it is not the patient-centred therapist’s task to remove these feelings: The task is simply to stay with the patient’s experiences. 
The resilience of patients is the key of healing.
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}

%PCA理論
治療關係的核心條件: 說好話 眼對眼 engaging 用真心
以心印心 engaging
身心相連 body-mind connection
捨末求本
身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，
「他自己本身」就具有療癒效果
「把自己當藥方開出去」

@@

%% why holistic? 太極 氣功 情緒 myofascia and sympathetic system
中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
養生和治療的原則:
一、某些病症可以透過食療而改善的會建議自行調養
二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
四、沒有一勞永逸的食療，不宜執著特定的食療神話
五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
六、認識自己身體的狀態比吸收營養資訊更重要
七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
情志養生 悲喜憂思苦 七情
人俯仰於天地之間
順從四季氣候變化
保養正氣陶冶性情
自我療癒身心靈疾病
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生
每位醫師都可以成為「創傷知情者」
幫助我們身邊的病患， 懂他的心靈創傷
讓他有安全感， 才有機會改變疾病的走向

“每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）”
解說：
患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。

>>>>

%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of fear, depression, stress, anxiety, fatigue, sadness, it is not the patient-centred therapist’s task to remove these feelings: The task is simply to stay with the patient’s experiences. 
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
%PCA理論 by *** Tex Chi
%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
%以心印心 engaging
身心相連 body-mind connection
捨末求本 find the source
A holistic healthcare providers will engage his/her patients with eye-to-eye contact and mind-to-mind connection. Their compassion, empathy and sympathy is induced by suffering of their patients from those diseases. They treat patients by using medication, surgery, and "themselves"
The resilience of patients will be also induced by the holistic healthcare. % of healing.
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」
%Spirituality
%慈悲心 compassion 
%同情心 sympathy
%同理心 empathy
%non-verbal contact

@@

%% why holistic? 太極 氣功 情緒 myofascia and sympathetic system
中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
養生和治療的原則:
一、某些病症可以透過食療而改善的會建議自行調養
二、某些病症已需要醫療輔助的時候會建議醫食同時進行勿偏癈其一
三、某些病症需要醫療系統監控的時候會建議多找幾家醫院醫師綜合性評估
四、沒有一勞永逸的食療，不宜執著特定的食療神話
五、體質會變，所以變的是療法，而不是讓體質去適應固定療程
六、認識自己身體的狀態比吸收營養資訊更重要
七、沒有好或不好的飲食或療法，只有適不適合自身體質的療法
情志養生 悲喜憂思苦 七情
人俯仰於天地之間
順從四季氣候變化
保養正氣陶冶性情
自我療癒身心靈疾病
%自他不二 心存正念 向內看，解決苦之源
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念 慈悲
%5.心無恐懼: 情志養生
每位醫師都可以成為「創傷知情者」
幫助我們身邊的病患，懂他的心靈創傷，讓他有安全感， 才有機會改變疾病的走向

"每一位患者都有自癒能力， 我們知情之後， 也要逐步讓他本人知情， 看見之後， 在良好的「治療關係」中， 協助他們漸漸找回自己的療癒。（以他們自己的腳步）"
解說：
患者的自癒力就是復原力（resilience),  強調「治療關係」（安全、 信任、 分享權力、 自決） 以及”知情”(暸解過往創傷經驗對自身的影響，進而開始療癒的過程）的重要性。
